Refunctionalization of Abstracting Abstract Machines (Functional Pearl)

### 2018-03-16 paper.tex
Contributions

broadly speaking, AAM and ADI they are both abstract interpreters.

@@

the essence of abstracting definitional interpreter.

\begin{itemize}
\item The main contribution of this paper is filling the gap
  between small-step AAM and big-step ADI by developing a series of
  systematic transformations.
  The correspondence between abstract
  machines and interpreters exists not only in concrete semantics artifact,
  but also in abstract semantics artifact.
  Galois connection?

\item A new understanding of pushdown control-flow analysis by
  refunctionalization.
  We present an abstract interpreter obtained from refunctionalizing
  an small-step abstracting abstract machine.
  This abstract interpreter naturally enjoys pushdown control-flow property
  because the refunctionalization forces us to sequentialize the
  abstract execution.
  We also analyze its correctness, soundness and termination.

\item Further, we show that defunctionalization and refunctionalization
  of abstract interpreters play important roles for call stack of analyzed language.
  Given this insight, we reveal that why small-step AAM has no pushdown
  control-flow property (if without extra efforts), as well as explain
  that why ADI naturally extends pushdown control-flow property from its
  defining language.

>>>>

Abstracting abstract machines (AAMs) and abstract definitional interpreters (ADIs) are, broadly speaking, both examples of abstract interpreters. \note{JD: need more bullet points here and I can fill this in}

@@

% the essence of abstracting definitional interpreter.

We summarize our contributions as follows:

\begin{itemize}
\item The main contribution of this paper is the filling of the gap
  between small-step AAM and big-step ADI by developing a series of
  systematic transformations.
  We show that the correspondence between abstract
  machines and interpreters exists not only in concrete semantics artifact,
  but also in abstract semantics artifact.
  Galois connection?
  \note{JD: Section number?}

\item A new understanding of pushdown control-flow analysis by
  refunctionalization.
  We present an abstract interpreter obtained from refunctionalizing
  a small-step abstracting abstract machine.
  This abstract interpreter naturally exhibits the pushdown control-flow property,
  as the refunctionalization forces us to sequentialize the
  abstract execution.
  We also analyze its correctness, soundness, and termination.

\item Further, we show that defunctionalization and refunctionalization
  of abstract interpreters play important roles for the call stack of the analyzed language.
  Given this insight, we reveal precisely \emph{why} small-step AAM has no pushdown
  control-flow property (without extra efforts), as well as explain
  why ADI naturally extends pushdown control-flow property from its
  defining language.
